---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Linkage Regularization 

Given a list of nodes, edge distances, and weights updates edges to propagate information through the network.

Inputs are variable in a data frame `df_edges` with the following columns: 

- `node1`, `node2`: a pair of linked nodes.
- `node1_weight`, `node2_weight` node weight: a measure of how well measured that test is. Lower
  weights means the node should move more.
- `edge`: the distance between two nodes.
- `weight`: how well measured the `edge` is. Lower weights mean
  that edge should move more.
  
Three regularization techniques

- Triangle regularization:
  - Uses `edge` and edge `weight`
  - updates until all cyclic graphs between any 3 nodes is a valid
    triangle where the longest side is shorter than the sum of the other
    two sides.
- Gravity regularization (not implemented)
  - Uses `edge` and `node1_weight`, `node2_weight`
  - The closer two nodes are, the more strongly they will pull together.
    I need to think about how to implement this, seems like it will be
    problematic and will converge to a solution of a couple of node
    clusters that are very distant from each other.
- Spring regularization:
  - Uses `edge`, edge `weight`, and `node1_weight`, `node2_weight`
  - Simulate a network of springs that each want to collapse to a length
    of 0 - spring strength is `edge` X `weight` (maybe this should be
    inverse normed `weight`?). Uses node weights to distribute spring forces
    among connected nodes. The further apart two nodes are, the harder
    the spring will pull them together.


<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of Triangle Regularization from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("williamlief/triangleRegularization")
```

## Triangle Regularization Examples

### A single triangle
This is a basic example with a valid triangle, no updates are made. Note that the edge length labels are NOT proportional to the graphed length - this is necessary because we will be showing invalid triangles, that is, cases where you can't close the shape with the listed edge lengths. 

```{r example_tr_valid, figures-side, fig.show="hold", out.width="50%"}
library(triangleRegularization)

df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge,
    "a", "b", 1,
    "a", "c", 1,
    "b", "c", 2
  )

layout <- save_layout(df_edges)
tris <- get_triangles(df_edges)

triangle_plot(df_edges, tris, layout, main = "input graph")
update <- learn_polys(df_edges, tris)
triangle_plot(update, tris, layout, main = "updated graph")

```

Now we have an invalid triangle and we update it to be valid. We are implicitly using equal weights here, so the long side and the short sides are all adjusted by the same amount.

```{r example_tr_invalid, figures-side, fig.show="hold", out.width="50%"}
df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge,
    "a", "b", 1,
    "a", "c", 1,
    "b", "c", 3
  )

layout <- save_layout(df_edges)
tris <- get_triangles(df_edges)

triangle_plot(df_edges, tris, layout, main = "input graph")
update <- learn_polys(df_edges, tris)
triangle_plot(update, tris, layout, main = "updated graph")

```

### Multiple Triangles
Now we have a mix of valid and invalid triangles, with shared edges. 

```{r example_tr_with_square, figures-side, fig.show="hold", out.width="50%"}
df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge,
    "a", "b", 1,
    "a", "c", 1,
    "a", "d", 4,
    "b", "c", 3,
    "b", "d", 2,
    "c", "d", 2
  )

layout <- save_layout(df_edges)
tris <- get_triangles(df_edges)

triangle_plot(df_edges, tris, layout, main = "input graph")
update <- learn_polys(df_edges, tris)
triangle_plot(update, tris, layout, main = "updated graph")
```

And finally here is a complex example

```{r example_tr_complex, figures-side, fig.show="hold", out.width="50%"}

df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge,
    "a", "b", 1,
    "a", "c", 1,
    "a", "d", 4,
    "b", "c", 3,
    "b", "d", 2,
    "c", "d", 2,
    "a", "e", 1,
    "b", "e", 5,
    "a", "f", 6,
    "e", "f", 4,
    "c", "g", 4,
    "d", "g", 1
  )

layout <- save_layout(df_edges)
tris <- get_triangles(df_edges)

triangle_plot(df_edges, tris, layout, main = "input graph")
update <- learn_polys(df_edges, tris)
triangle_plot(update, tris, layout, main = "updated graph")
```

### Using Weights

You can also include a `weight` column in df_edges. The weights column will be normalized within each triangle as `w = w/sum(w)`. Edges with larger weights will be adjusted proportionally less than edges with smaller weights. 

```{r example_tr_weights, figures-side, fig.show="hold", out.width="50%"}
df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge, ~weight,
    "a", "b", 1, 1,
    "a", "c", 1, 1,
    "b", "c", 3, 4
  )

layout <- save_layout(df_edges)
tris <- get_triangles(df_edges)

triangle_plot(df_edges, tris, layout, main = "input graph")
update <- learn_polys(df_edges, tris, use_weights = TRUE)
triangle_plot(update, tris, layout, main = "updated graph")
```

## Spring Regularization Examples

First a simple example with 3 nodes in a line. Note that the plot only shows the edge weights. Because all the edges and weights are the same, the two springs are balanced and no updates occur. 

```{r example_sp_3node_line, figures-side, fig.show="hold", out.width="50%"}

df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge, ~weight, ~node1_weight, ~node2_weight,
    "a", "a1", 1, 1, 1, 1,
    "a1", "b1", 1, 1, 1, 1,
  )

layout <- save_layout(df_edges)

spring_plot(df_edges, layout = layout, main = "input graph")
update <- learn_spring(df_edges)$df_edges
spring_plot(update, layout, main = "updated graph")

```


Now we have four nodes connected in a line.  In this example, even though the input data has all equal weights and distances, the network updates as the two outer edges contract and pull apart the middle edge. 

```{r example_sp_4node_line, figures-side, fig.show="hold", out.width="50%"}

df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge, ~weight, ~node1_weight, ~node2_weight,
    "a", "a1", 1, 1, 1, 1,
    "a1", "b1", 1, 1, 1, 1,
    "b1", "b", 1, 1, 1, 1,
  )

layout <- save_layout(df_edges)

spring_plot(df_edges, layout = layout, main = "input graph")
update <- learn_spring(df_edges)$df_edges
spring_plot(update, layout, main = "updated graph")

```

Here we have a complex example with a lot of connected nodes of varying weights.In this example, we've set node weights such that node a = 1 and node g = 7, and have alternated edge weights of 1 and 2. We can see that there are potentially very large changes in edge values. Look at the triangle AEF as an example of large shifts.

```{r example_sp_complex, figures-side, fig.show="hold", out.width="50%"}

df_edges <-
  tidyr::tribble(
    ~node1, ~node2, ~edge, ~weight, ~node1_weight, ~node2_weight,
    "a", "b", 1, 1, 1, 2,
    "a", "c", 1, 2, 1, 3,
    "a", "d", 4, 1, 1, 4,
    "b", "c", 3, 2, 2, 3,
    "b", "d", 2, 1, 2, 4,
    "c", "d", 2, 2, 3, 4,
    "a", "e", 1, 1, 1, 5,
    "b", "e", 5, 2, 2, 5,
    "a", "f", 6, 1, 1, 6,
    "e", "f", 4, 2, 5, 6,
    "c", "g", 4, 1, 3, 7, 
    "d", "g", 1, 2, 4, 7,
  )

layout <- save_layout(df_edges)

spring_plot(df_edges, layout = layout, main = "input graph")
update <- learn_spring(df_edges)$df_edges
spring_plot(update, layout, main = "updated graph")
```
